Designing a high-performance boundary element library with OpenCL and Numba

### 2021-04-13 intro.tex
finish expanding intro

This proved a burden when efforts started to modernize the library to be able to make better use of single-instruction-multiple-data (SIMD) optimization on CPUs and offload computation to GPUs. In 2018, we decided to rewrite the computational core from scratch. The aims were to support explicit SIMD optimization on CPUs with various instruction lengths, be able to offload computations to AMD, Intel, and Nvidia GPUs, and to base the complete codebase on Python. These aims naturally led to the choice of building a Python library based around OpenCL (using the PyOpenCL interface) and Numba.

At the end of 2019, we released the first version (0.1) of Bempp-cl \cite{Bempp-cl}. This was followed later in 2020 by version 0.2, the first release that we considered feature complete and mature for application use. Since then we have used Bempp-cl in a number of practical applications and many of our users are migrating to it from the old C++ based Bempp. In this article, we want to discuss the design choices behind Bempp-cl and provide a number of performance benchmarks on different compute devices, including CPUs, AMD, Intel, and Nvidia GPUs.

[To be continued with some more details about content and overview of the Sections]

@@

>>>>

At the end of 2019, we completed the main steps of a full rewrite of Bempp and released the first version (0.1) of Bempp-cl \cite{Bempp-cl}. This was followed later in 2020 by version 0.2, the first release that we considered feature complete and mature for application use. Since then we have used Bempp-cl in a number of practical applications and many of our users are migrating to it from the old C++ based Bempp. In this article, we discuss the motivation for the rewrite and restructure of Bempp and the reasoning behind the design choices we made when writing Bempp-cl.

@@

\bigskip

We begin this article by giving an overview of the boundary element method, and looking at how Bempp can be used to implement such problems. Following this, we discuss the implementation of boundary element kernels using OpenCL in more detail, and provide a number of performance benchmarks on different compute devices, including CPUs, AMD, Intel, and Nvidia GPUs.
